Parsing Tweets into Universal Dependencies

### 2018-02-01 naacl2018_rebuttal.txt

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17-tag tagset and we will revise our wording in the next version.

- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"

You are correct; this statement needs to be revised. What we should have said is that UD tokenisation treats each syntactic word as a unit of annotation. We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna to gon na) and treat them as new tokens. It is the same as UD conventions. However, we only use the "goeswith" relation to resolve multi-token words, where UD adopts both strategies of combining them back and using "goeswith" relation.
